\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-04-20 ase20/abstract.tex
[ASE] five -> four in abstract

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based
Semantics Extraction Toolchain.  It is the first tool that \textit{automatically
synthesizes} parsers and AST-IR translators directly from a given
language specification, ECMAScript.
For syntax, we develop a parser generation technique with \textit{lookahead
parsing} for \( \bnfes \), a variant of the extended BNF used in ECMAScript.
For semantics, \( \tool \) synthesizes AST-IR translators using \textit{forward
compatible} rule-based compilation.  \textit{Compile rules} describe how to
convert each step of abstract algorithms written in a structured natural language
into \( \ires \), an Intermediate Representation that we designed for
ECMAScript.  For the five most recent ECMAScript versions, \( \tool \) automatically
synthesized parsers for all versions, and compiled \inred{XX.XX}\% of the
algorithm steps on average.  After we complete the missing parts manually,
the extracted core semantics of the latest ECMAScript version (ES10, 2019)
passed all \inred{XX,XXX} applicable tests.
Using this \textit{first formal semantics of modern JavaScript}, we found
\inred{X} specification errors in ES10, which were all confirmed by
the Ecma Technical Committee 39.  Furthermore, we also successfully
applied \( \tool \) to \inred{X} feature proposals that are ready
for inclusion in the next ECMAScript, 
which shows the forward compatibility of \( \tool \).
\end{abstract}

>>>>

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based
Semantics Extraction Toolchain.  It is the first tool that \textit{automatically
synthesizes} parsers and AST-IR translators directly from a given
language specification, ECMAScript.
For syntax, we develop a parser generation technique with \textit{lookahead
parsing} for \( \bnfes \), a variant of the extended BNF used in ECMAScript.
For semantics, \( \tool \) synthesizes AST-IR translators using \textit{forward
compatible} rule-based compilation.  \textit{Compile rules} describe how to
convert each step of abstract algorithms written in a structured natural language
into \( \ires \), an Intermediate Representation that we designed for
ECMAScript.  For the four most recent ECMAScript versions, \( \tool \) automatically
synthesized parsers for all versions, and compiled \inred{XX.XX}\% of the
algorithm steps on average.  After we complete the missing parts manually,
the extracted core semantics of the latest ECMAScript version (ES10, 2019)
passed all \inred{XX,XXX} applicable tests.
Using this \textit{first formal semantics of modern JavaScript}, we found
\inred{X} specification errors in ES10, which were all confirmed by
the Ecma Technical Committee 39.  Furthermore, we also successfully
applied \( \tool \) to \inred{X} feature proposals that are ready
for inclusion in the next ECMAScript, 
which shows the forward compatibility of \( \tool \).
\end{abstract}
